### 2015-11-20 section/5_exper.tex
fix ~0

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $\sim$0           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $\sim$0       &   /           & 142.29{\bf X} \\
      GCC27733    & $\sim$0        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $\sim$0           & $\sim$0        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $\sim$0       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable.}
  \label{tab:performance}
\end{table}

\comment{
\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
                       & {\bf Resultless} &  \multicolumn{2}{c}{\bf C-L R. } & \multicolumn{2}{c}{\bf C-I R.}\\
      \cmidrule(lr){3-4}    
      \cmidrule(lr){5-6}   
     {\bf BugID}       &                & Not               &  S.+O.            & Not                & S.+O.  \\
     \midrule
     Mozilla347306     & 1.07\%         & 303.37{\bf X}     &  22.40\%       & 467.74{\bf X}         & 10.17\%      \\
     Mozilla416628     & 0.80\%         & 56.51{\bf X}      &  4.10\%        & 84.6{\bf X}           & 2.99\%\\
     \midrule
     MySQL27287        & $\sim$0        & 108.55{\bf X}     &  1.66\%        & 351.07{\bf X}         & - \\
     MySQL15811        &  -             & 226.04{\bf X}     &  0.03\%        & 423.44{\bf X}         & - \\
     \midrule
      GCC46401         & 3.12\%         & 20.07{\bf X}      &  3.80\%        & 37.44{\bf X}          & 5.95\%\\ 
      GCC1687          & -              & /                 &  /             & 141.29{\bf X}         & $\sim$0 \\
      GCC27733         & $\sim$0        & /                 &  /             & 16.41{\bf X}          & 4.73\%         \\
      GCC8805          & -              & 1.22{\bf X}       & $\sim$0        & 2.52{\bf X}           & $\sim$0\\
      GCC21430         & -              & 106.20{\bf X}     & 5.46\%         & 158.89{\bf X}         & 0.69\%\\
      GCC12322         & -              & 20.07{\bf X}      & 1.75\%         & 37.44{\bf X}          & $\sim$0\\
  \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop. 
    Only performance results from non-extracted benchmarks are shown here. 
  Not: not applying the performance optimization in \Tool.
  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
  /: not applicable. }
  \label{tab:performance}
\end{table}
}

>>>>

\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
	    & \multicolumn{3}{c}{\Tool w/ optimization} & \multicolumn{2}{c}{w/o optimization} \\
     \cmidrule(lr){2-4}
     \cmidrule(lr){5-6}
     {\bf BugID}  & {\bf Resultless}  &  {\bf C-L R. } & {\bf C-I R. }  & {\bf C-L R.}  & {\bf C-I R. } \\
    \midrule
    Mozilla347306 &  1.07\%           &  22.40\%       &  10.17\%       & 304.37{\bf X} & 468.74{\bf X} \\ 
    Mozilla416628 &  0.80\%           &  4.10\%        &  2.99\%        & 567.51{\bf X} & 85.6{\bf X} \\
    \midrule
     MySQL27287   & $<$0.01\%           &   1.66\%       &   -            & 109.55{\bf X} & 352.07{\bf X} \\
     MySQL15811   &  -                &   0.03\%       &   -            & 227.04{\bf X} & 424.44{\bf X} \\
    \midrule
      GCC46401    & 3.12\%         & 3.80\%            &  5.95\%        & 21.07{\bf X}  & 38.44{\bf X}\\ 
      GCC1687     & -              & /                 &  $<$0.01\%       &   /           & 142.29{\bf X} \\
      GCC27733    & $<$0.01\%        & /                 &  4.73\%        &   /           & 17.41{\bf X}     \\
      GCC8805     & -              & $<$0.01\%           & $<$0.01\%        & 2.22{\bf X}   &  3.52{\bf X}\\
      GCC21430    & -              & 5.46\%            &   0.69\%       & 107.20{\bf X} & 159.89{\bf X} \\
      GCC12322    & -              & 1.75\%            &  $<$0.01\%       & 21.07{\bf X}  & 38.44{\bf X} \\
   \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop
    (only non-extracted benchmarks are shown). 
  -: dynamic analysis is not needed;
  /: not applicable.}
  \label{tab:performance}
\end{table}

\comment{
\begin{table}
  \centering
  \scriptsize
  \newcommand{\Yes}[1]{\checkmark{}$_#1$}
  \newcommand{\No}[0]{-}
  \begin{tabular}{lccccc}
    \toprule
                       & {\bf Resultless} &  \multicolumn{2}{c}{\bf C-L R. } & \multicolumn{2}{c}{\bf C-I R.}\\
      \cmidrule(lr){3-4}    
      \cmidrule(lr){5-6}   
     {\bf BugID}       &                & Not               &  S.+O.            & Not                & S.+O.  \\
     \midrule
     Mozilla347306     & 1.07\%         & 303.37{\bf X}     &  22.40\%       & 467.74{\bf X}         & 10.17\%      \\
     Mozilla416628     & 0.80\%         & 56.51{\bf X}      &  4.10\%        & 84.6{\bf X}           & 2.99\%\\
     \midrule
     MySQL27287        & $sim$0        & 108.55{\bf X}     &  1.66\%        & 351.07{\bf X}         & - \\
     MySQL15811        &  -             & 226.04{\bf X}     &  0.03\%        & 423.44{\bf X}         & - \\
     \midrule
      GCC46401         & 3.12\%         & 20.07{\bf X}      &  3.80\%        & 37.44{\bf X}          & 5.95\%\\ 
      GCC1687          & -              & /                 &  /             & 141.29{\bf X}         & $\sim$0 \\
      GCC27733         & $\sim$0        & /                 &  /             & 16.41{\bf X}          & 4.73\%         \\
      GCC8805          & -              & 1.22{\bf X}       & $\sim$0        & 2.52{\bf X}           & $\sim$0\\
      GCC21430         & -              & 106.20{\bf X}     & 5.46\%         & 158.89{\bf X}         & 0.69\%\\
      GCC12322         & -              & 20.07{\bf X}      & 1.75\%         & 37.44{\bf X}          & $\sim$0\\
  \bottomrule
   \end{tabular}
  %\nocaptionrule
  \caption{Run-time overhead of applying \Tool to the buggy loop. 
    Only performance results from non-extracted benchmarks are shown here. 
  Not: not applying the performance optimization in \Tool.
  -: static analysis can figure out the results and hence no dynamic analysis is conducted.
  /: not applicable. }
  \label{tab:performance}
\end{table}
}
